Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-05-15 files/Chapter3/dynamicconvergence.tex
Chapter 2.4.2 and 4.2
Chapter 7

\subsection{Error estimates}\label{e_est}
Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$. It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$.

@@

The authors of \cite{BV13} use interpolation theory to determine the error $e_p$. However to obtain an error estimate for $e$ is not trivial. The approach of the authors is to use Finite Element Analysis to obtain an error estimate for $e$.\\

Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\

>>>>

\subsection{Error estimates}\label{e_est}
Under the assumptions \textbf{A1}-\textbf{A4} of Section 2 and continuity of $f$, there exists unique solutions for Problem GVar and Problem GVar$^h$. The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar. This is proven the main result of \cite{BV13}.

@@

The authors of \cite{BV13} mention that interpolation theory can be used to determine the error $e_p$. However to obtain an error estimate for $e$ is not as trivial. This is where the authors use the Finite Element Analysis, which is used to obtain an error estimate for $e$.

Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.

### 2023-05-15 files/Chapter7/Beam.tex
Chapter 7

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
This section is a literature study of the article \cite{LVV09}. The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams. In the real world, a beam is a complex three-dimensional model. So a three-dimensional model would be a good approximation and better than a one-dimensional model. It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.\\

@@

Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.\\

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
In the article \cite{LVV09}, the authors show that the Timoshenko beam theory is a feasible model to use in practical applications of beams. In this section, the article is studied and the results are replicated.

Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.

This section is a literature study of the article \cite{LVV09}. The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams. In the real world, a beam is a complex three-dimensional model. So a three-dimensional model would be a good approximation and better than a one-dimensional model. It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.

@@

### 2023-05-15 files/Chapter7/Introduction.tex
Chapter 7

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate. Validity in this context refer to how well the solutions compare to the solutions of more realistic higher dimensional models.\\

@@

\begin{itemize}
	\item[-] Section 7.2: Comparison between the cantilever Timoshenko beam and cantilever two-dimensional beam.
	\item[-] Section 7.3: Comparison between the cantilever two-dimensional beam and cantilever three-dimensional beams.
	\item[-] Section 7.4: Comparison between the cantilever Reissner-Mindlin plate and cantilever three-dimensional plate.
\end{itemize}

In Section 7.2, the work in \cite{LVV09} is discussed and the numerical results are verified. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. More results not given in  [LVV09] are also calculated, to be used in the sections following.\\

Section 7.3 is a natural extension of the article \cite{LVV09}. In this section, the validity of a two-dimensional beam model is investigated. The results of the two-dimensional beam are compared to a three-dimensional beam. The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.\\

Section 7.4 extends the work of \cite{LVV09} to plate models. Specifically a comparison of a cantilever two-dimensional Reissner-Mindlin plate to a cantilever three-dimensional plate.\\

@@

\end{document}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate model for practical applications. Validity in this context refers to how well the solutions of the model compare to the solutions of more realistic higher-dimensional model.

@@

Section 7.2 is a discussion and a verification of numerical results of the work done in \cite{LVV09} In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. We also include some extra results for different values of the parameter $\alpha$.

Section 7.3 is a natural extension of the article \cite{LVV09} which is mentioned by the authors. In this section, the validity of the two-dimensional beam model use in Section 7.2 is investigated. The results of the two-dimensional beam are compared to a three-dimensional beam.

The two-dimensional beam is an intermediate step to validate the Timoshenko beam model. A direct comparison between the one and three dimensional would be preferred, but the authors of \cite{LVV09} mention that this will introduce complexities, which will be discussed in more detail in the numerical results.

Section 7.4 extends the work of \cite{LVV09} further to plate models. Specifically a comparison of a cantilever two-dimensional Reissner-Mindlin plate to a cantilever three-dimensional plate.

@@

\subsubsection{Global Parameters}
The models in this Chapter (and this dissertation) assume the use of an identical isotropic material with, a rectangular cross-section. These are defined in global parameters shared by all the models. The parameters are as follows:

\begin{itemize}
    \item Elastic modulus ($G$): This is calculated using the formula $G = \frac{E}{2(1+\nu)}$, where $E$ is the modulus of elasticity and $\nu$ is Poisson's ratio.

    \item Shear correction factor ($\kappa^2$): This is set to $5/6$, which is common for rectangular cross-sections.

    \item Poisson's ratio ($\nu$): This is set to $0.3$, a typical value for materials like steel used in engineering.
\end{itemize}

The consistent use of these parameters across all models helps to ensure that any differences in the results can be attributed to the model structures themselves, rather than variations in the material or geometric properties.
\end{document}
